---
title: 'Lab 0: Lab template'
subtitle: "STATS 369"
author: "This task does NOT need to be submitted"
output:
  html_document:
    highlight: pygments
    theme: readable
    toc: true
    toc_depth: 2
    toc_float: true
---

*It is good practice to have all your general set up at the start of your document. Imagine this is the beginning of a new Rmd. This is where I would set any general chunk options, as well as where I would load my libraries. If I realise I need additional libraries later, I would come back here and add them.*

*Notes from me are in italics.*

```{r setup, message = FALSE}
# Set code to show
knitr::opts_chunk$set(echo = TRUE)

# Load libraries
library(tidyverse)

```

## Task 1

*Use headings to organise your submission and make it easy for your marker to find your answers*

```{r}
# Is the hashtag/octothrope is inside a code chunk, then it is a comment
# You will be expected to comment your code sufficiently clearly
# so that others with reasonable R knowledge could follow your work
```


## Task 2

An example of some commentary about my work...

```{r}
# Some commented code
x = 2+2
```

The result of my calculation is `r x`. That is some inline R code being run!

I can also multiply by 10 to get `r x*10`.

## References

*Not all labs/assignment will need references, but if you use a generative AI, you will need to reference that each time.*

*You may use whatever referencing style you prefer (I have used APA here for the references for this lab). We will not be marking for perfect style, but it should fufil the purpose of making your sources clear and enabling others to find your original source in a scholarly way.*

Horst, A. (2019). [A glam rock band comprised of 3 fuzzy round monsters labeled as "Text", "Outputs" and "Code" performing together. Stylized title text reads: "R Markdown - we’re getting the band back together."]. https://allisonhorst.com/r-packages-functions

OpenAI. (2023). ChatGPT (Mar 14 version) [Large language model]. https://chat.openai.com/chat

